Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
It's \ja, not \cite

Unfortunately, the field of signal-based ecoacoustics is still in infancy. \ja{We still haven't strictly defined what ``ecouacoustics'' is. Is there a simple, short definition we can use somewhere before this?}
As a consequence, few well-built datasets are readily available for evaluation purposes.
A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data. \cite{So what's the difference between ecoacoustics and acoustic scene classification?}
While narrower in its range of applications, it has the advantage of being rooted in cognitive psychology of categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of several well-designed datasets.

>>>>

Unfortunately, the field of signal-based ecoacoustics is still in infancy. \ja{We still haven't strictly defined what ``ecouacoustics'' is. Is there a simple, short definition we can use somewhere before this?}
As a consequence, few well-built datasets are readily available for evaluation purposes.
A closely related, and more mature, field of investigation is the classification of acoustic scenes, where the aim is to predict labels by processing audio data. \ja{So what's the difference between ecoacoustics and acoustic scene classification?}
While narrower in its range of applications, it has the advantage of being rooted in cognitive psychology of categorization \cite{dubois2006cognitive, maffiolo_caracterisation_1999, guastavino_ideal_2006} and has received the attention of the data mining community for some time, resulting in the availability of several well-designed datasets.
